The helicoverpa package

### 2018-08-27 notebook/helicoverpa_notes.Rmd
Update notes

     - **AUG** [13](#u-13-AUG-2018), [14](#u-14-AUG-2018)
     - **JUL** [18](#u-18-JUL-2018), [23](#u-23-JUL-2018), [30](#u-30-JUL-2018)

@@

>>>>

     - **AUG** [13](#u-13-AUG-2018), [14](#u-14-AUG-2018), [27](#u-27-AUG-2018)
     - **JUL** [18](#u-18-JUL-2018), [23](#u-23-JUL-2018), [30](#u-30-JUL-2018)

@@

> <a name="u-27-AUG-2018">Update: 27 AUG 2018</a>

```{r, echo = FALSE}
# ==============================================================================
# This is just a toy version of the model, for the presentation
# ==============================================================================
# Note that I'm adding 'toy' at the start of each function; this is just in case
# we actually want to keep some of these functions in the eventual R package, 
# but also don't want to worry about not being able to name functions like
# "initialise_land" the same here as elsewhere in the eventual bigger model.
# ==============================================================================
toy_simulate_resistance <- function(generations = 20,       # Generations to sim
                                    xdim = 2,               # Land dimension 1
                                    ydim = 2,               # Land dimension 2
                                    pathogens = 1,          # Pathogen strains
                                    crops = 1,              # Crop species
                                    path_alleles = 3,       # Pathogen alleles
                                    crop_alleles = 3,       # Crop alleles
                                    pest_init = 2000,       # Initial pests 
                                    crop_rotate = "static", # Crops rotated
                                    path_rotate = "static", # Pathogens rotated
                                    pest_move_pr = 0.1,     # Pest movement
                                    pest_move_dist = 1,     # Pest move distance
                                    fecundity = 8,          # Offspring per fem
                                    cell_K = 2000           # K per cell
                                    ){

results_to_json <- function(sim, filename = "sim.json"){
    if("package:jsonlite" %in% search() == FALSE){
        stop("Error: Need to load the R package 'jsonlite'")
    }
    colnames(sim) <- c("ID", "sex", "xloc", "yloc", "p_al_1", "p_al_2", 
                       "c_al_1", "c_al_2");
    modsim <- list( traits = colnames(sim), 
                    values = unname(apply(sim, 1, 
                                          function(x) as.data.frame(t(x))))
              );
    sim_json <- toJSON(list(traits = names(modsim), values = modsim), 
                   pretty = TRUE);                   
    write(sim_json, filename);
    return(sim_json);
}

**Transferring simulation results to json**

I've written a short bit of code to link the simulation results to the code. The input for this is a single *generation* of the model (this could be easily changed). So if we run the `toy_simulate_resistance` function [as before](#u-14-AUG-2018), we get a list with elements being each generation.

```{r}
sim <- toy_simulate_resistance(crops = 3, pathogens = 3);
```

We can look at just the last generation below.

```{r}
head(sim[[19]]);
```

The code below sticks all of this into the json format (for the one generation), prints the json output to a file if `printit == TRUE`, and returns the json output.

```{r}
results_to_json <- function(sim, printit = TRUE, filename = "sim.json"){
    if("package:jsonlite" %in% search() == FALSE){
        stop("Error: Need to load the R package 'jsonlite'")
    }
    colnames(sim) <- c("ID", "sex", "xloc", "yloc", "p_al_1", "p_al_2", 
                       "c_al_1", "c_al_2");
    modsim <- list( traits = colnames(sim), 
                    values = unname(apply(sim, 1, 
                                          function(x) as.data.frame(t(x))))
              );
    sim_json <- toJSON(list(traits = names(modsim), values = modsim), 
                   pretty = TRUE);
    if(printit == TRUE){
        write(sim_json, filename);
    }
    return(sim_json);
}
```

Using the function below to print and return the json. This relies on the `jsonlite` package, which must be installed and loaded.

```{r}
library(jsonlite);
sim_json <- results_to_json(sim = sim[[19]], 
                            filename = "../data/sample_sim.json");
```

The `sim_json` output should be easy to modify as necessary. I've not added it here because it's much too large for the notebook, but it can be accessed on the dev branch in the file [sample_sim.json](https://github.com/bradduthie/helicoverpa/blob/dev/data/sample_sim.json).
